### 2023-04-10 main/chapter_theory.tex
write some lagrangian for mssm

>>>>

\subsection{Lagrangian formulation}
\label{sec:theory_susy_lagrangian}
In Section~\ref{sec:theory_sm_lagrangian}, we presented a highly compressed
summary of the Standard Model Lagrangian.
Despite its minimality, the MSSM is a far more complicated theory than the
Standard Model, and the expression of its Lagrangian formulation is
far larger.
This section therefore presents and even more compressed summary of the
Lagrangian formulation of the MSSM.

Although any viable theory must include the Standard Model in an appropriate
appropriation, the Standard Model's Lagrangian need not be explicitly included.
Indeed, it is not convenient to express the MSSM's Lagrangian as an add-on to
the Standard Model. It stands alone.

A convenient first decomposition of the MSSM Lagrangian's parts splits it into
four parts:
\begin{equation}
\mathcal{L}_\mathrm{MSSM} =
\mathcal{L}_\mathrm{SUSY}
+ \mathcal{L}_\mathrm{soft}
+ \mathcal{L}_\mathrm{gf}
+ \mathcal{L}_\mathrm{ghost}
,
\end{equation}
in which
$\mathcal{L}_\mathrm{SUSY}$ is the supersymmetric part,
$\mathcal{L}_\mathrm{soft}$ is the a `softly' breaking part
(which is necessary because supersymmetry is not an unbroken symmetry of
nature),
and
$\mathcal{L}_\mathrm{gf}$ and $\mathcal{L}_\mathrm{ghost}$
are two additions that are necessary for quantization of the
theory~\cite{kuroda1999complete}.

\paragraph{Supersymmetry.}
The supersymmetric summand $\mathcal{L}_\mathrm{SUSY}$ contains numerous terms
that implement the main particle content of the MSSM.
These terms are not trivially expressed as Lagrangian densities in
four-dimensional spacetime, but are more fundamentally also integrated over
`superspace' coordinates~\cite{martin2016primer, kuroda1999complete}.
It contains kinetic terms for the gauge bosons, gauginos, fermions, sfermions,
Higgs, and higgsinos fields.
It also implements interactions between these fields,
including interactions between the fermions and gauge bosons,
Yukawa interactions between the fermions and Higgs fields and higgsinos,
and interactions between the gauge bosons and Higgs fields.
The gauge-Higgs interactions produce masses for the gauge bosons.
Other terms directly implement masses for mixtures of the higgsino fields.

\paragraph{Soft breaking.}
With no known mechanism for supersymmetry breaking,
the term $\mathcal{L}_\mathrm{soft}$ is expressed as a maximally general form
with $30$ free parameters, which have only weak constraints to ensure
symmetries in the theory.
It includes possible mass terms for the constituent fields, as well as scalar
interaction vertices.

\paragraph{Others.}
The gauge-fixing term $\mathcal{L}_\mathrm{gf}$ ensures that the gauge boson
propagators take the Standard Model form.
The ghost term $\mathcal{L}_\mathrm{ghost}$ introduces special scalar fields
that interact with bosons in the theory, but which have no effect at tree-level
but are necessary for self-consistency of the theory in loop diagrams.

\subsection{Specific simplified models}
\TODO{C1N2 and GMSB for $\twoljets$}

\TODO{Cross-sections}
